Joint Satellite Distributions in the Milky Way and Andromeda

### 2017-09-24 paper/paper.tex
updated randomized points presentation
paper text

\section{Observational Characterists of Andromeda and the Milky Way}
\label{sec:obs}

@@

\begin{figure*}
\centering
\includegraphics[width=0.7\textwidth]{planewidth_lg.pdf}
\includegraphics[width=0.7\textwidth]{ba_ratio_lg.pdf}
\includegraphics[width=0.7\textwidth]{ca_ratio_lg.pdf}
\includegraphics[width=0.7\textwidth]{mu_lg.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:general}}
\end{figure*}

@@

We characterize the bright ($M_V<-9$) satellite spatial distribution
with four different metrics.

\begin{enumerate}
\item{The inertia tensor}.
\item{Fitting planes}.
\item{Velocity Anisotropy}.
\end{enumerate}

I what follows we describe the details of implementation of each
metric.

\subsection{Inertia Tensor}
\label{sub:inertia}
First, by computing the inertia tensor defined as

\begin{equation}
{\bf{\bar{I}}} = \sum_{k \in V}[(\bf{r}_i - \bf{r}_0)^2\cdot \bf{1} -
  (\bf{r}_i-\bf{r}_0)\cdot (\bf{r}_i - \bf{r}_0)^{T}],
\end{equation}
%
where $k$ indexes the set of satellites of interest
$\bf{r}_k$ are the satellites' positions, $\bf{r}_{0}$ is the
positions pof the host DM halo, $\bf{1}$ is the unit matrix,  and
${\bf r}^T$ is the transposed vector $\bf{r}$. 
We finally compute the eigenvalues, $a>b>c$, and corresponding
eigenvectors, $\hat{I}_a$, $\hat{I}_b$, $\hat{I}_c$, of this tensor.
In the case of a sheet-like configuration the vector perpendicular to
the sheet would be signaled by, $\hat{I}_a$, the eigenvector of the
largest eigenvalue.

@@

\subsection{Plane fitting}
\label{sub:planes}

We fit satellite planes around each galaxy in the pair by randomly
generating 10000 unit vectors homogeneously distributed over the
sphere.
Each vector represents the direction perpendicular to a plane passing through
the main galaxy's center of mass. 
We compute the dot product of this unit vector with the position vector
for each satellite, this gives us the satellite distances to the
plane. 
The best plane is determined by the vector that gives the lowest
sample standard deviation in the satellite distances to the plane.
In the set of unit vectors to be considered we also include the vector
$\hat{I}_a$, which provides the exact solution in the case of $3$
satallites. 
We take the sample standard deviation as a measure of the plane's width
and denote by $\hat{p}$ the unit vector defining the direction
perpendicular to the best plane.
We also store the median of the satellite distances to the plane as a
measure of the plane's location with respect to the central galaxy.

\subsection{Velocity Anisotropy}
\label{sub:beta}

The velocity anisotropy paramenter, $\beta$ is defined as

\begin{equation}
  \beta = 1 - \frac{\sum_i v^2_{\rm{tan}; i}}{2\sum_i v^{2}_{\rm{rad};i}},
\label{eq:beta}
\end{equation}
% 
where $v_{\rm{tan/rad};i}$ correspond to the tangential/radial
velocity of the $i$-th satellite with respect to the central galaxy.

\begin{table*}
  \centering
\begin{tabular}{lll}
\hline\hline
Symbol & Units & Description\\\hline
$M_{\star}$ & $10^{10}$\Msun & Stellar mass of the central galaxy\\
$N_s$ & & Number of satellites with $M_V<-9$\\
$a > b> c$ & & Inertia tensor eigenvalues. \\
$\hat{I}_a$, $\hat{I}_b$, $\hat{I}_c$ & & Inertia tensor eigenvectors. \\
$\beta$  &  & Satellite Velocity Anisotropy\\
$\sigma_s$ & kpc & Plane width\\
$\hat{r}_{AB}$& & Unit vector in the direction to the galaxy companion\\
\hline\hline
\end{tabular}
  \caption{Overview of the parameters computed for each central galaxy
    and its satellite system.
  \label{tab:models}}
\end{table*}

>>>>

\section{Observational Data}
\label{sec:obs}

@@

\begin{figure*}
\centering
\includegraphics[width=0.7\textwidth]{mu_lg.pdf}
\includegraphics[width=0.7\textwidth]{planewidth_lg.pdf}
\includegraphics[width=0.7\textwidth]{ca_ratio_lg.pdf}
\includegraphics[width=0.7\textwidth]{ba_ratio_lg.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:general}}
\end{figure*}

@@

We use the inertia tensor to characterize the satellites.
This tensor is defined as

\begin{equation}
{\bf{\bar{I}}} = \sum_{k \in V}[(\bf{r}_i - \bf{r}_0)^2\cdot \bf{1} -
  (\bf{r}_i-\bf{r}_0)\cdot (\bf{r}_i - \bf{r}_0)^{T}],
\end{equation}
%
where $k$ indexes the set of satellites of interest
$\bf{r}_k$ are the satellites' positions, $\bf{r}_{0}$ is the
positions pof the host DM halo, $\bf{1}$ is the unit matrix,  and
${\bf r}^T$ is the transposed vector $\bf{r}$. 
We finally compute the eigenvalues, $a>b>c$, and corresponding
eigenvectors, $\hat{I}_a$, $\hat{I}_b$, $\hat{I}_c$, of this tensor.
In the case of a sheet-like configuration the vector perpendicular to
the sheet would be signaled by, $\hat{I}_a$, the eigenvector of the
largest eigenvalue. 
We measure the width of the satellite distribution as the standard
deviation of all satellite distances to the plane defined by the
vector $\hat{I}_a$.

@@

\begin{table*}
  \centering
\begin{tabular}{lll}
\hline\hline
Symbol & Units & Description\\\hline
$\hat{r}_{AB}$& & Unit vector along the direction connecting two
dominant galaxies\\
$N_s$ & & Number of satellites\\
$a > b> c$ & & Inertia tensor eigenvalues. \\
$\hat{I}_a$, $\hat{I}_b$, $\hat{I}_c$ & & Inertia tensor eigenvectors. \\
$\sigma_s$ & kpc & Ellipsoid width\\

\hline\hline
\end{tabular}
  \caption{Overview of the parameters computed for each central galaxy
    and its satellite system.
  \label{tab:models}}
\end{table*}
